\documentclass[titlepage]{article}

\usepackage{tabularx}
\usepackage{booktabs}
\usepackage[bottom=3cm, right=3cm, left=3cm, top=3cm]{geometry}
\usepackage{graphicx}
\usepackage{hyperref}
\usepackage{float}
\newcommand\tab[1][1cm]{\hspace*{#1}}

\title{COMPSCI 4NL3: Natural Language Processing\\
Annotation Guidelines}

\author{Team 4\\
\\ Junnan Li
\\ Nawaal Fatima
\\ Rashad Bhuiyan
\\ Sumanya Gulati}                  

\date{02 February 2025}

\begin{document}

\begin{titlepage}
  \maketitle
\end{titlepage}

\newpage

\section{Annotation Guidelines}
Below are the guidelines developed for the annotation process and agreed upon 
by the annotators. Note that these guidelines have been specifically developed for 
annotating interview responses from asapsports and should not be directly used to
annotate other types of text before considering and adapting to relevant contexts and media. 
All examples provided here are related to NBA or WNBA interview responses.

\section{Labels and Defintions}
The labels are divided into the classes \textbf{focus} and \textbf{sentiment}. Focus can be either of 
the two labels - individual or team and similarly, sentiment can be either positive or negative. 
Focus has to do with whether the response focuses on the \emph{individual (self)} or the \emph{team} and 
Sentiment is based on whether the speaker is expressing \emph{positive} or \emph{negative} emotion.

\section{Rules}
For annotating focus, think about whether the coach/player emphasizes teamwork or individual contributions.
If both are true then the stronger instance should apply or the one that comes first if they are equally 
represented. For annotating sentiment, think about the tone coach/player is trying to convey. If they are 
excited, hopeful, or showing a growth-mindset this would be considered positive. However, if the response 
is lacking confidence or conveys disappointment, this would be labelled negative.

\textbf{add}: only put 1 or Y for the labels that are applicable.

\section{Case Examples}
\begin{enumerate}
    \item Yeah, we are not down. We're positive. This is a group that believes. We didn't get an opportunity to get a 
    split or win two here on the road. Now Boston held serve. Now we've got to go home and hold serve.
    \begin{itemize}
        \item \textbf{Assigned Labels: Positive, Team}
    \end{itemize}
    This has been labelled positive as the overall sentiment is hopeful. They mention that they are not down and that this is 
    a group that believes in themselves so they are determined to win. 'We' has been used multiple times when talking about 
    their attitude so this is a sign of a team-focused mentality.

    \item Big. The small things, you know, we have to do the small things, and that's part of the game. Those are points 
    that we left on the board, and we didn't shoot free throws well tonight, and we have to be better.
    \begin{itemize}
        \item \textbf{Assigned Labels: Negative, Team}
    \end{itemize}
    This has been labelled negative as they say mention how they didn't do well which cost them points on the board. It shows 
    disapointment and a desire to improve. It is also team-focused as they are talking about the entire team as a collective 
    and not any single player.

    \item Yeah, I think Luka is a special player. He's one of, if not the best player in the world, and he causes a problem. 
    He's able to find guys. Again, creating open opportunities, and we just didn't take advantage of it.
    \begin{itemize}
        \item \textbf{Assigned Labels: Positive, Individual}
    \end{itemize}
    This has been labelled positive as they are complimenting a player. The comments are mainly focused on a singular player 
    and how they played thus it has been labelled individual.
\end{enumerate}

\section{Contact Information}
Please contact one of the following members of Team 4 for additional information and issue resolution:
\begin{itemize}
    \item Junnan Li: \textbf{lij499@mcmaster.ca}
    \item Nawaal Fatima: \textbf{fatimn8@mcmaster.ca}
    \item Rashad Bhuiyan: \textbf{bhuiyr2@mcmaster.ca}
    \item Sumanya Gulati: \textbf{gulats10@mcmaster.ca}
\end{itemize}

\end{document}